%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}
\chaptermark{acknowledgements}

% \begin{flushright}{\slshape
%     We have seen that computer programming is an art, \\
%     because it applies accumulated knowledge to the world, \\
%     because it requires skill and ingenuity, and especially \\
%     because it produces objects of beauty.} \\ \medskip
%     --- \defcitealias{knuth:1974}{Donald E. Knuth}\citetalias{knuth:1974} \citep{knuth:1974}
% \end{flushright}



\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax

\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{\tocEntry{Acknowledgments}}

First of all, I would like to express my gratitude to my supervisor Dr. Fabian Walter. He is the most helpful and nice supervisor I could have imagined. I could not know what would happen when I stepped into his office seven and a half years ago on the look for potential Bachelor thesis projects. The academic work and personal relationship between supervisor and student turned out so inspiring that I could have done only worse when searching for another supervisor for my Master's and PhD theses. Over the years, I have always left his office with new hope in times of trouble, the feeling that it all will work and anything is possible.

At this stage, I would also like to thank my friend Dr. Miguel Querejeta for showing me around at MPIA. If not for him, I might have never ended up on the mountain and certainly not in the group of Fabian.

Thank you to all my friends and colleagues at MPIA for the helpful discussions, mutual support and all the fun.

Astrophysical research is a joint effort of many people. Thank you to my colleagues and collaborators in various projects over the years.
A special thanks I want to address to Dr. J\"urgen Ott at NRAO who was my first academic contact outside MPIA seven years ago, whom I visited numerous time and a close collaborator ever since. Thank you for the great times in Socorro and, not to forget, for letting me borrow your car.

I would like to thank the members of my thesis committee who are also the referees of my thesis, Prof. Dr. Hans-Walter Rix and Prof. Dr. Ralf Klessen, for their time and support.
Thank you to Prof. Dr. Eva Grebel and Prof. Dr. Bj\"orn-Malte Sch\"afer for kindly agreeing to be members of the thesis defense committee.

\vspace{\baselineskip}

Life is much more than just work, as interesting as it might be. Athletics has always played a major role in my life and contributed so many things to me and my life.
Thank you to all my friends at USC Heidelberg and TSG 78 Heidelberg who helped me to maintain a healthy balance between work, sports and other activities. Training sessions, competitions, training camp and all the other fun activities we did together helped me through the harder times of my thesis.

\vspace{\baselineskip}

I am deeply grateful for the support from my parents over the years. A vital element for this thesis to ever exist was their encouragement to follow my passion and study physics in Heidelberg. Thank you for your support in all aspects of my life.

\vspace{\baselineskip}

Thank you Sophia for your unconditional love, for the practical and emotional support, especially, during the stressful times towards the end of my thesis.


\endgroup


\newpage
\chaptermark{}