%*******************************************************
% Publications
%*******************************************************
\pdfbookmark[1]{Publications}{publications}
\chapter*{Publications}
\chaptermark{publications}
\addcontentsline{toc}{chapter}{\tocEntry{Publications}}


During my PhD studies I was leading or contributing author of the following publications. The work presented in Chapters~\ref{chapter: outflow}, \ref{chapter: SSCs} and \ref{chapter: dendro} has been presented in Krieger et al. (2019), Krieger et al. (2020a) and Krieger et al. (2020b), respectively.


\vspace{\baselineskip}\textbf{\textsc{Leading author:}}
\vspace{0.5\baselineskip}

\publication{
    \textbf{N. Krieger}, A. D. Bolatto, A. K. Leroy, R. C. Levy, E. A.C. Mills, D. S. Meier, S. Veilleux, F. Walter, A. Weiß
    }{
    The Molecular ISM in the Super Star Clusters of the Starburst NGC253.
    }{
    2020a, submitted to The Astrophysical Journal
    }

\publication{
    \textbf{N. Krieger}, A. D. Bolatto, E. W. Koch, A. K. Leroy, E. Rosolowsky, F. Walter, A. Weiß, D. J. Eden, R. C. Levy, D. S. Meier, E. A. C. Mills, Toby Moore, Jürgen Ott, Yang Su, S. Veilleux
    }{
    The turbulent gas structure in the centers of NGC253 and the Milky Way.
    }{
    2020b, submitted to The Astrophysical Journal
    }

\publication{
    \textbf{N. Krieger}, A. D. Bolatto, F. Walter, A. K. Leroy, L. K. Zschaechner, D. S Meier, J. Ott, A. Weiss, E. A. C. Mills, R. C. Levy, S. Veilleux, M. Gorski.
    }{
    The Molecular Outflow in \ngc253 at a Resolution of Two Parsecs.
    }{
    The Astrophysical Journal, 2019 vol. 881 (1) p. 43.
    }

\publication{
    \textbf{N. Krieger}, J. Ott, H. Beuther, F. Walter, J. M. D. Kruijssen, D. S. Meier, E. A. C. Mills, Y. Contreras, P. Edwards, A. Ginsburg, C. Henkel, J. D. Henshaw, J. M. Jackson, J. Kauffmann, S. N. Longmore, S. Martín, M. R. Morris, T. Pillai, M. Rickert, E. Rosolowsky, H. Shinnaga, A. Walsh, F. Yusef-Zadeh, Q. Zhang.
    }{
    The Survey of Water and Ammonia in the Galactic Center (SWAG): Molecular Cloud Evolution in the Central Molecular Zone.
    }{
    The Astrophysical Journal, 2017 vol. 850 (1) p. 77.
    }


\vspace{\baselineskip}\textbf{\textsc{Contributing author:}}
\vspace{0.5\baselineskip}

\publication{
    K. L. Emig, A. D. Bolatto, A. K. Leroy, E. A. C. Mills, M. J. Jimenez Donaire, A. G. G. M. Tielens, L. Levy, \textbf{N. Krieger}, E. Ostriker, E. Rosolowsky,  S. Veilleux
    }{
    Star Clusters in the Central Starburst of \ngc4945
    }{
    Submitted to the The Astrophysical Journal
    }

\publication{
    J. M. D. Kruijssen, J. E. Dale, S. N. Longmore, D. L. Walker, J. D. Henshaw, S. M. R. Jeffreson, M. A. Petkova, A. Ginsburg, A. T. Barnes, C. D. Battersby, K. Immer, J. M. Jackson, E. R. Keto, \textbf{N. Krieger}, E. A C Mills, A. Sánchez-Monge, A. Schmiedeke, S. T. Suri, Q. Zhang.
    }{
    The dynamical evolution of molecular clouds near the Galactic Centre - II. Spatial structure and kinematics of simulated clouds.
    }{
    Monthly Notices of the Royal Astronomical Society, 2019 vol. 484 (4) pp. 5734-5754.
    }
    
\publication{    
    A. K. Leroy, A. D. Bolatto, E. C. Ostriker, F. Walter, M. Gorski, A. Ginsburg, \textbf{N. Krieger}, R. C. Levy, D. S. Meier, E. A. C. Mills, J. Ott, E. Rosolowsky, T. A. Thompson, S. Veilleux L. K. Zschaechner.
    }{
    Forming Super Star Clusters in the Central Starburst of NGC 253.
    }{
    The Astrophysical Journal, 2018 vol. 869 (2) p. 126.
    }
    
\publication{    
    L. K. Zschaechner, A. D. Bolatto, F. Walter, A. K. Leroy, C. Herrera, \textbf{N. Krieger}, J. M. D. Kruijssen, D. S Meier, E. A C Mills, J. Ott, S. Veilleux, A. Weiß.
    }{
    Spatially Resolved 12CO(2–1)/12CO(1–0) in the Starburst Galaxy NGC 253: Assessing Optical Depth to Constrain the Molecular Mass Outflow Rate.
    }{
    The Astrophysical Journal, 2018 vol. 867 (2) p. 111.
    }


\vspace{\baselineskip}\textbf{\textsc{Conference Proceedings:}}
\vspace{0.5\baselineskip}

\publication{    
    J. Ott, D. S Meier, A. Ginsburg, F. Yusef-Zadeh, \textbf{N. Krieger}, C. Jäschke.
    }{
    SWAG: Distribution and Kinematics of an Obscured AGB Population toward the Galactic Center.
    }{
    Proceedings IAU Symposium No. 343: Why Galaxies Care About AGB Stars: A Continuing Challenge through Cosmic Time, 2019, pp. 485-486.
    }

\publication{
    J. Ott, D. S Meier, \textbf{N. Krieger}, A. Ginsburg, T. Candelaria.
    }{
    Survey of Water and Ammonia in the Galactic center (SWAG): Morphologies of Molecular Tracers.
    }{
    Proceedings American Astronomical Society Meeting No. 233, 2019, p. 267.01.
    }
    
\publication{    
    J. Ott, \textbf{N. Krieger}, M. Rickert, D. S Meier, A. Ginsburg, F. Yusef-Zadeh.
    }{SWAG Water Masers in the Galactic Center.
    }{
    Proceedings IAU Symposium No. 336: Astrophysical Masers: Unlocking the Mysteries of the Universe, 2017
    }
    
\publication{    
    M. Rickert, F. Yusef-Zadeh, J. Ott, D. S Meier, \textbf{N. Krieger}.
    }{
    High Resolution Surveys of the Water and Methanol Star Formation Masers in the Central Molecular Zone.
    }{
    Proceedings American Astronomical Society Meeting No. 229, 2017, p. 216.06.
    }
    
\publication{    
    \textbf{N. Krieger}, J. Ott, F. Walter, J. M. D. Kruijssen, H. Beuther.
    }{
    Temperature Evolution of Molecular Clouds in the Central Molecular Zone.
    }{
    Proceedings IAU Symposium No. 322: The Multi-Messenger Astrophysics of the Galactic Centre, 2016, pp. 1-2.
    }
    
\publication{    
    J. Ott, D. S Meier, \textbf{N. Krieger}, M. Rickert.
    }{
    SWAG: Survey of Water and Ammonia in the Galactic Center.
    }{
    Proceedings IAU Symposium No. 322: The Multi-Messenger Astrophysics of the Galactic Centre, 2016, pp. 1-2.
    }
